---
title: "Analyze free-choice image norming experiment"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
This notebook analyzes the results of the norm_pics_freechoice experiment, where participants used 3 adjs to describe imgs of people they saw. They were also asked qs on location (where person was from), occupation, and how they think the person spoke (v. open-ended questions). 

```{r}
library(dplyr)
library(tidyr)
library(stringr)
library(tm)
library(wordcloud)
library(ggplot2)
library(lmerTest)
library(datapasta)
library(lexicon)
library(cowplot)
library(ggpubr)
library(dutchmasters)
library(stargazer)
library(textdata)

fullPalette <- c("#394165", "#A65141")
toughPalette <- c("#394165")
valleyPalette <-c("#A65141")

theme_set(theme_minimal())
source("../../../shared_resources/get_glasgow_norms.R")
source("../../../shared_resources/helpers.R")

```

# Get data, tidy / clean data
```{r}
pilot <- read.csv('../data/raw/norm_imgs_freechoice_pilot-trials.csv')
free <- read.csv('../data/raw/norm_imgs_freechoice_full-trials.csv')

n_distinct(pilot$workerid)
n_distinct(free$workerid)

exclude_pilot_ids <- c(2,6)
pilot.tidy <- pilot %>%
  filter(!workerid  %in% exclude_pilot_ids)

exclude_ids <- c(4, 24, 49) # Based on qualitative determination: non-sensical answers, repeating training trial of old man, etc. 
free.clean <- free %>%
  filter(!workerid  %in% exclude_ids) 

pilot.tidy$age <- as.factor(pilot.tidy$age)
free.clean <- bind_rows(pilot.tidy, free.clean)

free.tidy <- free.clean %>%
  select(stim, workerid, adj1, adj2, adj3, occupation, howspeak, age, wherefrom, extra_descript)%>%
  mutate(persona = str_split_fixed(stim, '_', n=3)[,1], 
         head = str_split_fixed(stim, '_', n=3)[,2], 
         bod = str_split_fixed(stim, '_', n=3)[,3]) %>%
  mutate(adj1 = str_to_lower(adj1, locale = 'en'), 
         adj2 = str_to_lower(adj2, local = 'en'), 
         adj3 = str_to_lower(adj3, local = 'en'), 
         occupation = str_to_lower(occupation, local = 'en'), 
         howspeak = str_to_lower(howspeak, local = 'en'), 
         wherefrom = str_to_lower(wherefrom, local = 'en'))

summary(free)
sd(free$Answer.time_in_minutes)

n_distinct(free.clean$workerid)
n_distinct(pilot.tidy$workerid)

```


# ADJECTIVES

## wrangle
Frequency counts by persona (Tough or Valley), and freq counts relative to n of each persona judgments 
(i.e., how common was a particular adjective judgment for a particular persona )
```{r}
freecounter <- free.tidy %>%
  gather(adjorder, adj, adj1:adj3) %>%
  mutate(adj = gsub(' ', '', adj)) %>%
  group_by(persona)%>%
  count(adj)%>%
  mutate(total_judgments_persona = sum(n), freq = n/total_judgments_persona,
         adj = as.factor(adj))

```

Frequency counts by individual stim
```{r}
ind_adjs <- free.tidy %>%
  gather(adjorder, adj, adj1:adj3) %>%
  mutate(adj = gsub(' ', '', adj)) %>%
  group_by(stim)%>%
  count(adj) %>%
  mutate(total_judgments_stim = sum(n)) %>%
  mutate (freq = n/total_judgments_stim)
```


Unique and shared words
```{r}
# what words are shared by both?
freecounter.spread <- freecounter %>%
  select(-total_judgments_persona, -freq)%>%
  spread(persona, n) %>%
  mutate_all(~replace(., is.na(.), 0)) 

shared_words <- freecounter.spread %>%
  filter(t!= 0 & v != 0) %>%
  arrange(desc(t))
shared_words

# what words are unique to each persona?
unique_toughs <- freecounter.spread %>%
  filter(t!= 0 & v == 0) %>%
  rename(n = 't') %>%
  mutate(persona_type = 't') %>%
  select(-v) %>%
  arrange(desc(n))
unique_toughs

unique_valleys <- freecounter.spread %>%
  filter(t== 0 & v != 0)%>%
  rename(n = 'v') %>%
  mutate(persona_type = 'v') %>%
  select(-t) %>%
  arrange(desc(n))
unique_valleys
```

## Visualize top Tough and Valley words
```{r}
top15_unique_t <- unique_toughs[0:15,]
top15_unique_v <- unique_valleys[0:15,]

top15 <- bind_rows(top15_unique_t, top15_unique_v)

#viz
unique_t.bar <- top15_unique_t %>%
  ggplot(aes(x=reorder(adj, n), y=n, fill = persona_type))+
  geom_col(stat="identity")+
  coord_flip() +
   ggtitle("Tough adjectives") +
  xlab("Adjective") +
  ylab("No. of occurrences")+
  scale_fill_manual(values=toughPalette)+
  scale_y_continuous(breaks = seq(from = 1, to = 12, by = 1)) +
  theme(axis.text.x  = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_blank(),
        #axis.title.x = element_blank(),
        #axis.title.y = element_text(size = 12, face="bold"),
        axis.title.x = element_text(size = 12),
        legend.position = "none")
unique_t.bar



unique_v.bar <- top15_unique_v %>%
  ggplot(aes(x=reorder(adj, n), y=n, fill = persona_type))+
  geom_col(stat="identity")+
  coord_flip() +
  ggtitle("Valley Girl adjectives") +
  xlab("Adjective") +
  ylab("No. of occurrences")+
  scale_fill_manual(values=valleyPalette)+
  scale_y_continuous(breaks = seq(from = 1, to = 12, by = 1)) +
  theme(axis.text.x  = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_blank(),
        #axis.title.x = element_blank(),
        #axis.title.y = element_text(size = 12, face="bold"),
        axis.title.x = element_text(size = 12),
        legend.position = "none")
unique_v.bar

 theme(axis.title.x = element_blank(),
          axis.text.x = element_text(color="black", size=16),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(color="black", size=16),
          legend.title = element_text(color="black", size=16),
          legend.text = element_text(color="black", size=14),
          )

top15_adj.plot <- ggarrange(unique_t.bar, unique_v.bar)
top15_adj.plot

ggsave('../plots/top15_adjs.png', top15_adj.plot, width=9, height=3)
```



##  Quantify impressions with Glasgow Norms; model VAD and gender
```{r}
# get glasgow norms
norms <- norms %>% rename(adj = words)

free.tidy$persona <- as.factor(free.tidy$persona)
noncounted <- free.tidy %>%
  gather(adjorder, adj, adj1:adj3) %>%
  mutate(adj = gsub(' ', '', adj)) %>%
  group_by(persona) %>%
  select(stim, adjorder, adj, workerid)

norms_adjs <- right_join(norms, noncounted, by = 'adj')
norms_adjs <- norms_adjs %>% 
  filter(!is.na(length)) #get rid of those that dont have an entry in norms lexicon - this will exclude misspellings etc for time being
norms_adjs
norms_adjs$persona <- relevel(norms_adjs$persona, ref = 't')

#linear models for each dimension (W random effects)
gendr <- lmer(gend_mean ~ persona + (1|stim) , data = norms_adjs)
summary(gendr)

gendr <- lmer(gend_mean ~ persona + (1|stim) + (1|workerid) , data = norms_adjs)
summary(gendr)

arous <- lmer(arous_mean ~ persona + (1|stim), data = norms_adjs)
summary(arous)

val <- lmer(val_mean ~ persona + (1|stim)+ (1|workerid), data = norms_adjs)
summary(val)

dom <- lmer(dom_mean ~ persona + (1|stim)+ (1|workerid), data = norms_adjs)
summary(dom)

#Just as sanity check: a dv that really shouldn't differ across personas ('imageability' - how imaginable something is)
imag <- lmer(imag_mean ~ persona + (1|stim)+ (1|workerid), data = norms_adjs)
summary(imag)
```
nb - gender: 1 = female, 7= male 
arousal: 1 = dull, 7 = excited
valence: 1 = bad, 7 = good
dom: 1 = poweless, 7 = in control

Valley descriptors more female, higher arousal, higher valence, more 'dominant' (but DOM is correlated with VALENCE - "VAL × DOM (r = .68; the more positive a word is, the more it provokes feelings of dominance" - Glasgow Norms Scott et al")

### Plot the VAD/Gender ratings associated with Tough/Valley words

#### gender 
```{r}
gend.df <- norms_adjs %>%
  group_by(persona) %>%
  summarise(gendmean_allwords = mean(gend_mean), CI.Low = ci.low(gend_mean), CI.High = ci.high(gend_mean)) %>%
  mutate(YMin = gendmean_allwords - CI.Low, YMax = gendmean_allwords + CI.High)

gend.plot <- ggplot(gend.df, aes(x=persona, y= gendmean_allwords)) +
  geom_bar(stat = "identity", aes(fill = persona)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  scale_fill_manual(values=fullPalette, name = "Persona Type", breaks= c("t", "v"), labels = c("Tough", "Valley Girl"))+
  theme(
    legend.title = element_blank(),
    legend.text = element_text(size = 12),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 12),
    axis.title.x=element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank())+
  expand_limits(y=c(1, 9))+
  scale_y_continuous(breaks = seq(from = 1, to = 9, by = 1)) +
  ylab("Gender association (1 = feminine, 9 = masculine)")

gend.plot
```


#### valence
```{r}
valence.df <- norms_adjs %>%
  group_by(persona) %>%
  summarise(valence_allwords = mean(val_mean), CI.Low = ci.low(val_mean), CI.High = ci.high(val_mean)) %>%
  mutate(YMin = valence_allwords - CI.Low, YMax = valence_allwords + CI.High)

val.plot <- ggplot(valence.df, aes(x=persona, y= valence_allwords)) +
  geom_bar(stat = "identity", aes(fill = persona)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  scale_fill_manual(values=fullPalette, name = "Persona Type", breaks= c("t", "v"), labels = c("Tough", "Valley Girl"))+
  theme(
    legend.title = element_blank(),
    legend.text = element_text(size = 12),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 12),
    axis.title.x=element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank())+
  expand_limits(y=c(1, 9))+
  ylab("Valence (1 = negative, 9 = positive)")
val.plot
```

#### arousal
```{r}
arouse.df <- norms_adjs %>%
  group_by(persona) %>%
  summarise(arouse_allwords = mean(arous_mean), CI.Low = ci.low(arous_mean), CI.High = ci.high(arous_mean)) %>%
  mutate(YMin = arouse_allwords - CI.Low, YMax = arouse_allwords + CI.High)

arous.plot <- ggplot(arouse.df, aes(x=persona, y= arouse_allwords)) +
  geom_bar(stat = "identity", aes(fill = persona)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  scale_fill_manual(values=fullPalette, name = "Persona Type", breaks= c("t", "v"), labels = c("Tough", "Valley Girl"))+
  theme(
    legend.title = element_blank(),
    legend.text = element_text(size = 12),
    axis.title.y = element_text(size = 14),
    axis.text.y = element_text(size = 12),
    axis.title.x=element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank())+
  expand_limits(y=c(1, 9))+
  ylab("Arousal (1 = dull, 9 = excited)")
arous.plot

```

#### all in one plot
```{r}
vadjectives <- ggarrange (gend.plot, val.plot, arous.plot,
                   ncol = 3,
                   common.legend = TRUE, legend = "bottom")
vadjectives
ggsave('../plots/vadjectives.png', vadjectives, width =10, height =5)

```


# Where from? (where in the US are Ts/Vs perceived to be from?)
```{r}
#Tidy up free input (bin categories reasonably)
free.tidy$wherefrom <- as.factor(free.tidy$wherefrom)
levels(free.tidy$wherefrom)

free.tidy$wherefrom <- as.character(free.tidy$wherefrom)
free.tidy <- free.tidy %>%
  mutate(wherefrom.tidy = ifelse(wherefrom == 'american' | wherefrom ==  'united states', 'america',
                          ifelse(wherefrom == 'ca' | wherefrom == 'californa' | wherefrom == 'hollywood' | wherefrom == 'los angeles' | wherefrom == 'san francisco', 'california', 
                          ifelse(wherefrom == 'fl', 'florida',
                          ifelse(wherefrom == 'mi', 'michigan',
                          ifelse(wherefrom == "ma", 'massachusetts',
                          ifelse(wherefrom == "portland oregon" | wherefrom == "portland", "oregon",
                          ifelse(wherefrom == "washingston"| wherefrom == "seattle", "washington",
                          ifelse(wherefrom == "philadeplia", "pennsylvania",
                          ifelse(wherefrom == "chicago", "illinois",
                          ifelse(wherefrom ==  "atlanta", "georgia", 
                          ifelse(wherefrom == 'new york ' | wherefrom == "ny" |wherefrom == "new york, ny", 'new york', wherefrom))))))))))))
free.tidy$wherefrom.tidy <- as.factor(free.tidy$wherefrom.tidy)
levels(free.tidy$wherefrom.tidy)

places <- free.tidy %>%
  group_by(persona)%>%
  count(wherefrom.tidy) %>%
  mutate(total_place_judgments = sum(n)) %>%
  mutate (freq = n/total_place_judgments)
```

## Perceived origins by stim
```{r}
places.stim <- free.tidy %>%
  group_by(stim,persona)%>%
  count(wherefrom.tidy) %>%
  mutate(total_place_judgments_stim = sum(n)) %>%
  mutate (freq = n/total_place_judgments_stim)
  
bicoastal <- places.stim %>%
  filter(wherefrom.tidy == 'california' | wherefrom.tidy == 'new york') 

  ggplot(bicoastal, aes( x = stim, y = n, fill = wherefrom.tidy)) +
  geom_bar(stat = "identity", position = 'dodge') +
    theme(axis.text.x=element_text(angle = -270, hjust = 0)) 
  View(places.stim)
```

```{r}
free.tidy$wherefrom.tidy <- as.factor(free.tidy$wherefrom.tidy)
free.tidy$wherefrom.tidy <- relevel(free.tidy$wherefrom.tidy, ref = 'california')
free.tidy$persona <- as.factor(free.tidy$persona)
free.tidy$persona <- relevel(free.tidy$persona, ref = 't')
```

## Logistic regression models for being 'from' CA/NY
```{r}
where.df <- free.tidy %>%
  mutate(CA = ifelse(wherefrom.tidy == 'california', 1, 0), NY = ifelse(wherefrom.tidy == 'new york', 1, 0))
where.df

ca.mod <- glmer(CA ~ persona + (1|stim), family = binomial, data = where.df)
summary(ca.mod)
#Valleys are more likely than Toughs to be 'from' CA
ny.mod <- glmer(NY ~ persona + (1|stim), family = binomial, data = where.df)
summary(ny.mod)
```

# Perceived occupation 
(what do participants think Toughs and Valleys do for a living?)
```{r}
occupation <- free.tidy %>%
  group_by(persona)%>%
  count(occupation)

toughs_occ <- occupation %>%
  filter(persona == 't')

valls_occ <- occupation %>%
  filter(persona == 'v')

tocc_cloud <- wordcloud(toughs_occ$occupation, toughs_occ$n, min.freq = 1)
vocc_cloud <- wordcloud(valls_occ$occupation, valls_occ$n, min.freq = 1)

occupation.spread <- occupation%>%
  spread(persona, n) %>%
  mutate_all(~replace(., is.na(.), 0)) 

shared_occupation <- occupation.spread  %>%
  filter(t!= 0 & v != 0) %>%
  arrange(desc(t))

unique_toughs_occ <- occupation.spread  %>%
  filter(t!= 0 & v == 0) %>%
  rename(n = 't') %>%
  mutate(persona_type = 't') %>%
  select(-v) %>%
  arrange(desc(n))
unique_toughs_occ

unique_valleys_occ <- occupation.spread  %>%
  filter(t== 0 & v != 0)%>%
  rename(n = 'v') %>%
  mutate(persona_type = 'v') %>%
  select(-t) %>%
  arrange(desc(n))
unique_valleys_occ 
```

#Qualitatively code speaking styles
```{r}
write.csv(free.tidy, '../data/clean/freechoiceresponses_tocode.csv')
coded <- read.csv('../data/clean/freechoiceresponses_tocode.csv' , skip = 1)

coded.tidy <- coded %>%
  select(stim, persona, howspeak.1, vocalfry:prestige..socioeconomic.)
```

Speaking style results
- 2 mentions of creak ('vocal fry'), one each for a V and a T
- 4 mentions of valley girl (3V, 1T)
- 5 mentions of 'slang' (1V, 4T)
- Pitch: 5 mentions of low pitch (all T), 9 mentions of high pitch (all V)
